---
title: "VasCalc"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
runtime: shiny
---

```{r setup, include=FALSE}
library(flexdashboard)
library(dplyr)
library(scales)
library(kidney.epi)
```

AAA
=======================================================================

Inputs {.sidebar}
-----------------------------------------------------------------------


```{r}
sliderInput("age_a", "Patient Age", min = 18, max = 90, value = 45)
selectInput("sex_a", "Patient Sex",
 						 choices = list("Male" = 0,
 						 							 "Female" = 1))
sliderInput("diam_a", "Maximal Aorta Diameter", min = 30, max = 100, value = 55)
selectInput("symp_a", "Patient Symptoms",
						choices = list("Asymptomatic" = 0,
													 "Sympomatic" = 1,
													 "Ruptured" = 2))
selectInput("renalclamp_a", "Do you expect to clamp above both renals?",
						 choices = list("Unlikely" = 0,
						 							 "Likely" = 1))
selectInput("prioraorta_a", "Has the patient had prior aortic surgery?",
						choices = list("No" = 0,
													 "Yes" = 1))
selectInput("cad_a", "History of coronary artery disease",
  						 choices = list("None" =                                         0,
  						 							 "History of MI, asymptomatic or stable angina" = 1,
  						 							 "Unstable angina/MI within 6 months" =           2))
selectInput("chf_a", "Congestive Heart Failure",
  						 choices = list("None" =  0,
	  					 						    "Asymptomatic" = 1,
  						 							 "Symptomatic" = 2))
selectInput("stress_a", "Stress Test",
						 choices = list ("Not Performed" = 0,
						 								"Normal" = 1,
						 								"Abnormal" = 2))
selectInput("cvd_a", "Cerebrovascular Disease",
  						 choices = list("No" =  0,
	  					 						    "Yes" = 1))
selectInput("copd_a", "COPD",
			  			 choices = list("None" =                         0,
			  			 						    "Not treated or on medication" = 1,
			  			 						    "Home oxygen" =                  2))
selectInput("dm_a", "Diabetes",
						 choices = list("None" = 0,
						 							 "Diet Controlled" = 1,
						 							 "Noninsulin Medication" = 2,
						 							 "Insulin Dependent" = 3))
selectInput("esrd_a", "ESRD on Dialysis",
						 choices = list("No" = 0,
						 							 "Yes" = 1))
sliderInput("cr_a", "Creatinine (mg/dL), not on dialysis", min = 0.5, max = 4.0, value = 1.0)
```

[More Guidance about Input Variables](https://adam-mdmph.github.io/Risk-Prediction-Text/aaa.html#input-variables)

Row
----------------------------------------------

### Annual Rupture Risk

```{r}
rupture_risk = reactive({
	rupture_risk = ifelse(input$diam_a < 40, "0.3%",
												ifelse(input$diam_a < 50, "0.5-1.5%",
															 ifelse(input$diam_a < 60, "1-11%",
															 			 ifelse(input$diam_a < 70, "11-22%", ">30%"))))
	return(rupture_risk)
})

renderValueBox({
  rupture_risk = ifelse(input$symp_a > 0, "Unable to calculate", 
    						rupture_risk())
	valueBox(
    value = rupture_risk,
    icon = "fa-bomb",
    color = ifelse(input$symp_a > 0, "grey",
    							 ifelse(input$diam_a < 40, "green",
												ifelse(input$diam_a < 50, "green",
															 ifelse(input$diam_a < 60, "orange", "red"))))
  )
})
```

Row
--------------------------------------------------------------------------------

[Where did these numbers come from?](https://adam-mdmph.github.io/Risk-Prediction-Text/aaa.html#annual-rupture-risk)

Row
-----------------------------------------------

### EVAR In-hospital Mortality

```{r}
evar_mort_hosp = reactive({
	age_1 = ifelse(input$age_a > 75, 1, 0)
	sex_1 = ifelse(input$sex_a == 1, 1, 0)
	cad_1 = ifelse(input$cad_a > 0, 1, 0)
	cvd_1 = ifelse(input$cvd_a == 1, 1, 0)
	copd_1 = ifelse(input$copd_a > 0, 1, 0)
	ckd_1 = ifelse(input$cr_a >= 1.5 & input$cr_a <=2 & input$esrd_a == 0, 1, 0)
	ckd_2 = ifelse(input$cr_a > 2 | input$esrd_a == 1, 1, 0)
	diam_1 = ifelse(input$diam_a > 65, 1, 0)
	evar_term = -6.76 + 0.78*age_1 + 0.69*sex_1 + 0.56*cad_1 + 0.71*cvd_1 + 0.95*copd_1 + 
		0.89*ckd_1 + 1.31*ckd_2 + 0.91*diam_1
	evar_mort_hosp = round(
		1/(1+exp(-evar_term)),
		3)
	return(evar_mort_hosp)
})

renderValueBox({
  evar_mort_hosp_numb <- as.numeric(evar_mort_hosp())
  evar_mort_hosp = ifelse((input$prioraorta_a == 1 | input$symp_a > 0), "Unable to calculate", 
    						scales::percent(evar_mort_hosp(), accuracy = 0.1))
  valueBox(
    value = evar_mort_hosp,
    icon = "fa-syringe",
    color = ifelse((input$prioraorta_a == 1 | input$symp_a > 0), "grey",
    							 ifelse(evar_mort_hosp_numb > 0.3, "black", 
    							 ifelse(evar_mort_hosp_numb > 0.08, "red", 
    							 			 ifelse(evar_mort_hosp_numb > 0.01, "orange", "green"))))
  )
})
```

### Open AAA In-hospital Mortality

```{r}
open_mort_hosp = reactive({
	age_1 = ifelse(input$age_a > 75, 1, 0)
	sex_1 = ifelse(input$sex_a == 1, 1, 0)
	cad_1 = ifelse(input$cad_a > 0, 1, 0)
	cvd_1 = ifelse(input$cvd_a == 1, 1, 0)
	copd_1 = ifelse(input$copd_a > 0, 1, 0)
	ckd_1 = ifelse(input$cr_a >= 1.5 & input$cr_a <=2 & input$esrd_a == 0, 1, 0)
	ckd_2 = ifelse(input$cr_a > 2 | input$esrd_a == 1, 1, 0)
	diam_1 = ifelse(input$diam_a == 1, 1, 0)
	renalclamp_1 = ifelse(input$renalclamp_a == 1, 1, 0)
	renalclamp_2 = ifelse(input$renalclamp_a == 2, 1, 0)
	open_term = -6.76 + 0.78*age_1 + 0.69*sex_1 + 0.56*cad_1 + 0.71*cvd_1 + 0.95*copd_1 + 
		0.89*ckd_1 + 1.31*ckd_2 + 0.91*diam_1 + 1.08*renalclamp_1 + 1.905*renalclamp_2
	open_mort_hosp = round(
		1/(1+exp(-open_term)),
		3)
	return(open_mort_hosp)
})

renderValueBox({
  open_mort_hosp_numb <- as.numeric(open_mort_hosp())
  open_mort_hosp = ifelse((input$prioraorta_a == 1 | input$symp_a > 0), "Unable to calculate", 
    						scales::percent(open_mort_hosp(), accuracy = 0.1))
  valueBox(
    value = open_mort_hosp,
    icon = "fa-user-ninja",
    color = ifelse((input$prioraorta_a == 1 | input$symp_a  > 0), "grey",
    							 ifelse(open_mort_hosp_numb > 0.3, "black", 
    							 ifelse(open_mort_hosp_numb > 0.08, "red", 
    							 			 ifelse(open_mort_hosp_numb > 0.01, "orange", "green"))))
  )
})
```

Row
-------------------------------------------------------------------------------
[Where did these numbers come from?](https://adam-mdmph.github.io/Risk-Prediction-Text/aaa.html#in-hospital-postprocedural-mortality)

Row
-------------------------------------------------------------------------------

### EVAR POMI

```{r}
evar_pomi = reactive({
	age_1 = ifelse(input$age_a >= 60 & input$age_a < 70, 1, 0)
	age_2 = ifelse(input$age_a >= 70 & input$age_a < 80, 1, 0)
	age_3 = ifelse(input$age_a >= 80, 1, 0)
	ckd_1 = ifelse(input$cr_a > 1.8 & input$esrd_a != 1, 1, 0)
	ckd_2 = ifelse(input$esrd_a ==1, 1, 0)
	stress_1 = ifelse(input$stress_a == 1, 1, 0)
	stress_2 = ifelse(input$stress_a == 2, 1, 0)
	cad_1 = ifelse(input$cad_a == 1, 1, 0)
	cad_2 = ifelse(input$cad_a == 2, 1, 0)
	dm_1 = ifelse(input$dm_a == 1, 1, 0)
	dm_2 = ifelse(input$dm_a == 2, 1, 0)
	dm_3 = ifelse(input$dm_a == 3, 1, 0)
	chf_1 = ifelse(input$chf_a == 1, 1, 0)
	chf_2 = ifelse(input$chf_a == 2, 1, 0)
	evar_term = -5.82 + 0.17 + 0.44*age_1 + 0.64*age_2 + 1.10*age_3 + 0.76*ckd_1 + 0.64*ckd_2 + 
	-0.15*stress_1 + 0.46*stress_2 + 0.40*cad_1 + 0.76*cad_2 + 0.18*dm_1 + 0.20*dm_2 + 0.39*dm_3 
	0.44*chf_1 + 0.50*chf_2
	evar_pomi = round(
		1/(1+exp(-evar_term)),
		3)
	return(evar_pomi)
})

renderValueBox({
  evar_pomi_numb <- as.numeric(evar_pomi())
  evar_pomi = ifelse((input$prioraorta_a == 1 | input$symp_a == 2), "Unable to calculate", 
    						scales::percent(evar_pomi(), accuracy = 0.1))
  valueBox(
    value = evar_pomi,
     icon = "fa-heartbeat",
    color = ifelse((input$prioraorta_a == 1 | input$symp_a == 2), "grey",
    							 ifelse(evar_pomi_numb > 0.1, "red", 
    							 ifelse(evar_pomi_numb > 0.05, "orange", "green")))
  )
})
```

### Open AAA POMI

```{r}
open_pomi = reactive({
	age_1 = ifelse(input$age_a >= 60 & input$age_a < 70, 1, 0)
	age_2 = ifelse(input$age_a >= 70 & input$age_a < 80, 1, 0)
	age_3 = ifelse(input$age_a >= 80, 1, 0)
	ckd_1 = ifelse(input$cr_a > 1.8 & input$esrd_a != 1, 1, 0)
	ckd_2 = ifelse(input$esrd_a == 1, 1, 0)
	stress_1 = ifelse(input$stress_a == 1, 1, 0)
	stress_2 = ifelse(input$stress_a == 2, 1, 0)
	cad_1 = ifelse(input$cad_a == 1, 1, 0)
	cad_2 = ifelse(input$cad_a == 2, 1, 0)
	dm_1 = ifelse(input$dm_a == 1, 1, 0)
	dm_2 = ifelse(input$dm_a == 2, 1, 0)
	dm_3 = ifelse(input$dm_a == 3, 1, 0)
	chf_1 = ifelse(input$chf_a == 1, 1, 0)
	chf_2 = ifelse(input$chf_a == 2, 1, 0)
	open_term = -5.82 + 1.91 + 0.44*age_1 + 0.64*age_2 + 1.10*age_3 + 0.76*ckd_1 + 0.64*ckd_2 + 
	-0.15*stress_1 + 0.46*stress_2 + 0.40*cad_1 + 0.76*cad_2 + 0.18*dm_1 + 0.20*dm_2 + 0.39*dm_3 
	0.44*chf_1 + 0.50*chf_2
	open_pomi = round(
		1/(1+exp(-open_term)),
		3)
	return(open_pomi)
})

renderValueBox({
  open_pomi_numb <- as.numeric(open_pomi())
  open_pomi = ifelse((input$prioraorta_a == 1 | input$symp_a == 2), "Unable to calculate", 
    						scales::percent(open_pomi(), accuracy = 0.1))
  valueBox(
    value = open_pomi,
     icon = "fa-heartbeat",
    color = ifelse((input$prioraorta_a == 1 | input$symp_a == 2), "grey",
    							 ifelse(open_pomi_numb > 0.1, "red", 
    							 ifelse(open_pomi_numb > 0.05, "orange", "green")))
  )
})
```

Row
-------------------------------------------------------------------------------

[Where did these numbers come from?](https://adam-mdmph.github.io/Risk-Prediction-Text/aaa.html#post-operative-myocardial-infarcation)

CLTI
===============================================================================

Inputs {.sidebar}
-------------------------------------------------------------------------------

### Patient Details

```{r}
sliderInput("age_p", "Patient Age", min = 18, max = 90, value = 45)
selectInput("sex_p", "Patient Sex",
 						 choices = list("Male" = 0,
 						 							 "Female" = 1))
selectInput("race_p", "Patient Race",
  						 choices = list("White" =     0,
  						 							 "Black" = 1,
						 							    "Not white or black" = 2))
selectInput("indication_p", "Indication for Procedure",
	  					 choices = list("Rest pain" =   0,
		  				 							  "Tissue loss" = 1))
selectInput("dzlevel_p", "Level of Disease Requiring Treatment",
						choices = list("Aortoiliac" = 1,
													 "Femoropopliteal" = 2,
													 "Tibial" = 3),
						multiple = TRUE)
selectInput("cad_p", "History of coronary artery disease",
				   		 choices = list("None" =                                         0,
		  				 						    "History of MI, asymptomatic or stable angina" = 1,
	  					 							  "Unstable angina/MI within 6 months" =           2))
selectInput("chf_p", "Congestive Heart Failure",
  						 choices = list("No" =  0,
	  					 						    "Yes" = 1))
selectInput("stress_p", "Stress Test",
						 choices = list ("Not Performed" = 0,
						 								"Normal" = 1,
						 								"Abnormal" = 2))
selectInput("copd_p", "COPD",
			  			 choices = list("None" =                         0,
			  			 						    "Not treated or on medication" = 1,
			  			 						    "Home oxygen" =                  2))
selectInput("tob_p", "Smoking Status",
						choices = list("None" = 0,
													 "Prior History" = 1,
													 "Current" = 2))
selectInput("dm_p", "Diabetes",
						 choices = list("None" = 0,
						 							 "Diet Controlled" = 1,
						 							 "Noninsulin Medication" = 2,
						 							 "Insulin Dependent" = 3))
selectInput("esrd_p", "ESRD on Dialysis",
						 choices = list("No" = 0,
						 							 "Yes" = 1))
sliderInput("cr_p", "Creatinine (mg/dL), if not on dialysis", min = 0.5, max = 4.0, value = 1.0)
selectInput("amb_p", "Ambulation Status",
						   choices = list("Independent" =      0,
						 						     	"With Assistance" =  1,
						 							    "Wheelchair bound" = 2,
						 							    "Bedbound" =         3))
selectInput("preopmeds_p", "Preop Medications",
									 choices = list("Beta blocker" = 1,
									 							 "Antiplatelet" = 2,
									 							 "Statin" = 3),
						multiple = TRUE)
```

[More Guidance about Input Variables](https://adam-mdmph.github.io/Risk-Prediction-Text/clti.html#input-variables-1)

Row
----------------------------------------------------------

### 30d Mortality after infrainguinal revascularization

```{r}
clti_mort_30 = reactive({
	  age_1 = ifelse(input$age_p >= 60 & input$age_a <= 70, 1, 0)
	  age_2 = ifelse(input$age_p > 70 & input$age_a <= 80, 1, 0)
  	age_3 = ifelse(input$age_p > 80, 1, 0)
		race_1 = ifelse(input$race_p > 0, 1, 0)
		indication_1 = ifelse(input$indication_p == 1, 1, 0)
		tob_1 = ifelse(input$tob_p == 1, 1, 0)
		tob_2 = ifelse(input$tob_p == 2, 1, 0)
		cad_1 = ifelse(input$cad_p == 1, 1, 0)
		cad_2 = ifelse(input$cad_p == 2, 1, 0)
		chf_1 = ifelse(input$chf_p == 1, 1, 0)
		copd_1 = ifelse(input$copd_p == 1, 1, 0)
		copd_2 = ifelse(input$copd_p == 2, 1, 0)
		egfr = egfr.ckdepi (creatinine = input$cr_p, age = input$age_p, sex = input$sex_p, 
												ethnicity = input$race_p, creatinine_units = "mg/dl", 
												label_afroamerican = c ("1"), label_sex_male = c ("0"), 
												label_sex_female = c ("1")) 
		ckd_1 = ifelse((egfr >= 60 & egfr < 90) & input$esrd_p == 0, 1, 0)
		ckd_2 = ifelse((egfr >= 30 & egfr < 60) & input$esrd_p == 0, 1, 0)
		ckd_3 = ifelse((egfr >= 15 & egfr < 30) & input$esrd_p == 0, 1, 0)
		ckd_4 = ifelse(egfr < 15 | input$esrd_p == 1, 1, 0)
		amb_1 = ifelse(input$amb_p == 1, 1, 0)
		amb_2 = ifelse(input$amb_p == 2, 1, 0)
		amb_3 = ifelse(input$amb_p == 3, 1, 0)
		statin_1 = ifelse(3 %in% input$preopmeds_p, 1, 0)
		clti_term_30 = age_1*0.51 + age_2*0.97 + age_3*1.5 + race_1*-0.38 + indication_1*0.42 + cad_1*0.25 + 
			cad_2*0.78 + chf_1*0.53 + copd_1*0.27 + copd_2*0.86 + ckd_1*-0.05 + ckd_2*0.26 + ckd_3*0.76 + ckd_4*1.45 +
			amb_1*0.41 + amb_2*0.60 + amb_3*1.34 + statin_1*-0.29
		clti_mort_30 = round(
			(1-0.997^(exp(clti_term_30))),
			3)
	return(clti_mort_30)
})

renderValueBox({
  clti_mort_30_numb <- as.numeric(clti_mort_30())
  clti_mort_30 = ifelse(1 %in% input$dzlevel_p, "Unable to calculate", 
    						scales::percent(clti_mort_30(), accuracy = 0.1))
  valueBox(
    value = clti_mort_30,
    icon = "fa-skull",
    color = ifelse(1 %in% input$dzlevel_p, "grey",
    							 ifelse(clti_mort_30_numb > 0.1, "red", 
    										ifelse(clti_mort_30_numb > 0.05, "orange", "green")))
  )
})
```

### 2y Mortality after infrainguinal revascularization

```{r}
clti_mort_2y = reactive({
	  age_1 = ifelse(input$age_p >= 60 & input$age_a <= 70, 1, 0)
	  age_2 = ifelse(input$age_p > 70 & input$age_a <= 80, 1, 0)
  	age_3 = ifelse(input$age_p > 80, 1, 0)
		race_1 = ifelse(input$race_p > 0, 1, 0)
		indication_1 = ifelse(input$indication_p == 1, 1, 0)
		tob_1 = ifelse(input$tob_p == 1, 1, 0)
		tob_2 = ifelse(input$tob_p == 2, 1, 0)
		cad_1 = ifelse(input$cad_p == 1, 1, 0)
		cad_2 = ifelse(input$cad_p == 2, 1, 0)
		chf_1 = ifelse(input$chf_p == 1, 1, 0)
		copd_1 = ifelse(input$copd_p == 1, 1, 0)
		copd_2 = ifelse(input$copd_p == 2, 1, 0)
		egfr = egfr.ckdepi (creatinine = input$cr_p, age = input$age_p, sex = input$sex_p, ethnicity = input$race_p, 
												creatinine_units = "mg/dl", label_afroamerican = c ("1"), label_sex_male = c ("0"), 
												label_sex_female = c ("1")) 
		ckd_1 = ifelse((egfr >= 60 & egfr < 90) & input$esrd_p == 0, 1, 0)
		ckd_2 = ifelse((egfr >= 30 & egfr < 60) & input$esrd_p == 0, 1, 0)
		ckd_3 = ifelse((egfr >= 15 & egfr < 30) & input$esrd_p == 0, 1, 0)
		ckd_4 = ifelse(egfr < 15 | input$esrd_p == 1, 1, 0)
		amb_1 = ifelse(input$amb_p == 1, 1, 0)
		amb_2 = ifelse(input$amb_p == 2, 1, 0)
		amb_3 = ifelse(input$amb_p == 3, 1, 0)
		betablock_1 = ifelse(1 %in% input$preopmeds_p, 1, 0)
		antiplat_1 = ifelse(2 %in% input$preopmeds_p, 1, 0)
		statin_1 = ifelse(3 %in% input$preopmeds_p, 1, 0)
		clti_term_2y = age_1*0.32 + age_2*0.68 + age_3*1.17 + race_1*-0.25 + indication_1*0.43 + tob_1*0.09 +
			tob_2*0.11 + cad_1*0.18 + cad_2*0.31 + chf_1*0.49 + copd_1*0.24 + copd_2*0.52 + ckd_1*-0.02 + ckd_2*0.22 +
			ckd_3*0.64 + ckd_4*1.09 + amb_1*0.33 + amb_2*0.52 + amb_3*0.91 + betablock_1*0.12 + antiplat_1*-0.13 + 
			statin_1*-0.12
		clti_mort_2y = round(
			(1-0.952^(exp(clti_term_2y))),
			3)
	return(clti_mort_2y)
})

renderValueBox({
  clti_mort_2y_numb <- as.numeric(clti_mort_2y())
  clti_mort_2y = ifelse(1 %in% input$dzlevel_p, "Unable to calculate", 
    						scales::percent(clti_mort_2y(), accuracy = 0.1))
  valueBox(
    value = clti_mort_2y,
    icon = "fa-skull",
    color = ifelse(1 %in% input$dzlevel_p, "grey",
    							 ifelse(clti_mort_2y_numb > 0.1, "red", 
    										ifelse(clti_mort_2y_numb > 0.05, "orange", "green")))
  )
})
```

Row
-------------------------------------------------------------------------------

Simons, Jessica, Andres Schanzer, Julie Flahive, Nicholas Osborne, Joseph Mills, Andrew Bradbury, and Michael Conte. “Survival Prediction in Patients with Chronic Limb-Threatening Ischemia Who Undergo Infrainguinal Revascularization.” European Journal of Vascular and Endovascular Surgery 58 (2019): S120–34. https://doi.org/10.1016/j.ejvs.2019.04.009.

Row
-------------------------------------------------------------------------------

### Revascularization POMI

```{r}
p_pomi = reactive({
	age_1 = ifelse(input$age_p >= 60 & input$age_p < 70, 1, 0)
	age_2 = ifelse(input$age_p >= 70 & input$age_p < 80, 1, 0)
	age_3 = ifelse(input$age_p >= 80, 1, 0)
	ckd_1 = ifelse(input$cr_p > 1.8 & input$esrd_p != 1, 1, 0)
	ckd_2 = ifelse(input$esrd_p == 1, 1, 0)
	stress_1 = ifelse(input$stress_p == 1, 1, 0)
	stress_2 = ifelse(input$stress_p == 2, 1, 0)
	cad_1 = ifelse(input$cad_p == 1, 1, 0)
	cad_2 = ifelse(input$cad_p == 2, 1, 0)
	dm_1 = ifelse(input$dm_p == 1, 1, 0)
	dm_2 = ifelse(input$dm_p == 2, 1, 0)
	dm_3 = ifelse(input$dm_p == 3, 1, 0)
	chf_1 = ifelse(input$chf_p == 1, 1, 0)
	chf_2 = ifelse(input$chf_p == 2, 1, 0)
	proc = ifelse(1 %in% input$dzlevel_p, 1, 0)
	proc_1 = ifelse(proc == 0, 1, 0)
	proc_2 = ifelse(proc == 1, 1, 0)
	p_pomi_term = -5.82 + 1.12*proc_1 + 1.60*proc_2 + 0.44*age_1 + 0.64*age_2 + 1.10*age_3 + 0.76*ckd_1 + 0.64*ckd_2 + 
	  -0.15*stress_1 + 0.46*stress_2 + 0.40*cad_1 + 0.76*cad_2 + 0.18*dm_1 + 0.20*dm_2 + 0.39*dm_3 + 0.44*chf_1 + 
		0.50*chf_2
	p_pomi = round(
		1/(1+exp(-p_pomi_term)),
		3)
	return(p_pomi)
})

renderValueBox({
  p_pomi_numb <- as.numeric(p_pomi())
  valueBox(
    value = scales::percent(p_pomi(), accuracy = 0.1),
     icon = "fa-heartbeat",
    color = ifelse(p_pomi_numb > 0.1, "red", 
    							 ifelse(p_pomi_numb > 0.05, "orange", "green"))
  )
})
```

Row
-------------------------------------------------------------------------------

Bertges, Daniel J., Dan Neal, Andres Schanzer, Salvatore T. Scali, Philip P. Goodney, Jens Eldrup-Jorgensen, and Jack L. Cronenwett. “The Vascular Quality Initiative Cardiac Risk Index for Prediction of Myocardial Infarction after Vascular Surgery.” Journal of Vascular Surgery 64, no. 5 (November 2016): 1411-1421.e4. https://doi.org/10.1016/j.jvs.2016.04.045.

Row
-------------------------------------------------------------------------------


Carotid
==============================================================================

Input {.sidebar}
------------------------------------------------------------------------------

### Patient Details

```{r}
sliderInput("age_c", "Patient Age", min = 18, max = 90, value = 45)
selectInput("sex_c", "Patient Sex",
 						 choices = list("Male" = 0,
 						 							 "Female" = 1))
selectInput("pres_c", "Primary Symptomatic Event",
						choices = list("Asymptomatic" = 0,
													 "Monocular" = 1,
													 "Single Cerebral TIA" = 2,
													 "Multiple Cerebral TIA" = 3,
													 "Minor Stroke" = 4,
													 "Major Disabling Stroke" = 5))
sliderInput("time_c", "Time Since Last Event", min = 1, max = 180, value = 7)
selectInput("sten_c", "Percent Stenosis",
						choices = list("<50%" = 0,
						              "50-59" = 1,
													 "60-69%" = 2,
													 "70-79%" = 3,
													 "80-89%" = 4,
													 "90-99%" = 5,
													 "Near Occlusion" = 6,
													 "Occluded" = 7))
selectInput("ulc_c", "Ulcerated Plaque",
						choices = list("No" = 0,
													 "Yes" = 1))
selectInput("htn_c", "Hypertension on medications",
						choices = list("No" = 0,
													 "Yes" = 1))
selectInput("cad_c", "History of coronary artery disease",
  						 choices = list("None" =                                         0,
  						 							 "History of MI, asymptomatic or stable angina" = 1,
  						 							 "Unstable angina/MI within 6 months" =           2))
selectInput("chf_c", "Congestive Heart Failure",
  						 choices = list("None" =  0,
	  					 						    "Asymptomatic" = 1,
  						 							 "Symptomatic" = 2))
selectInput("stress_c", "Stress Test",
						 choices = list ("Not Performed" = 0,
						 								"Normal" = 1,
						 								"Abnormal" = 2))
selectInput("pvd_c", "Peripheral Vascular Disease",
  						 choices = list("No" =  0,
	  					 						    "Yes" = 1))
selectInput("copd_c", "COPD",
			  			 choices = list("None" =                         0,
			  			 						    "Not treated or on medication" = 1,
			  			 						    "Home oxygen" =                  2))
selectInput("dm_c", "Diabetes",
						 choices = list("None" = 0,
						 							 "Diet Controlled" = 1,
						 							 "Noninsulin Medication" = 2,
						 							 "Insulin Dependent" = 3))
selectInput("esrd_c", "ESRD on Dialysis",
						 choices = list("No" = 0,
						 							 "Yes" = 1))
sliderInput("ckd_c", "Creatinine (mg/dL), not on dialysis", min = 0.5, max = 4.0, value = 1.0)
```

[More Guidance about Input Variables](https://adam-mdmph.github.io/Risk-Prediction-Text/carotid.html#input-variables-2)

Row
-------------------------------------------------------------------------------

### 5-year risk of ipsilateral stroke (UNDER CONSTRUCTION)

```{r}
cva_5y = reactive({
	sten_1 = as.numeric(ifelse(input$sten_c < 6, input$sten_c, 0))
	nearocc_l = ifelse(input$sten_c == 6, 1, 0)
	sex_1 = ifelse(input$sex_c == 0, 1, 0)
	age_1 = as.numeric(input$age_c/10)
	time_1 = as.numeric(input$time_c/7)
	pres_1 = ifelse(input$pres_c == 2, 1, 0)
	pres_2 = ifelse(input$pres_c == 3, 1, 0)
	pres_3 = ifelse(input$pres_c == 4, 1, 0)
	pres_4 = ifelse(input$pres_c == 5, 1, 0)
	dm_1 = ifelse(input$dm_c > 0, 1, 0)
	cad_1 = ifelse(input$cad_c > 0, 1, 0)
	pvd_1 = ifelse(input$pvd_c == 1, 1, 0)
	htn_1 = ifelse(input$htn_c == 1, 1, 0)
	ulc_1 = ifelse(input$ulc_c == 1, 1, 0)
	cva_5y_term = -3.55 + log(1.18)*sten_1 + log(0.49)*nearocc_l + log(1.19)*sex_1 + log(1.12)*age_1 +
		log(0.96)*time_1 + log(1.41)*pres_1 + log(2.05)*pres_2 + log(1.82)*pres_3 + log(2.54)*pres_4 + log(1.35)*dm_1 +
		log(1.57)*cad_1 + log(1.24)*htn_1 + log(2.03)*ulc_1
	cva_5y = round(
		1/(1+exp(-cva_5y_term)),
		3)
	return(cva_5y)
})

renderValueBox({
  cva_5y_numb <- as.numeric(cva_5y())
  cva_5y = ifelse(input$sten_c == 7 | input$pres_c == 0, "Unable to calculate", 
    						scales::percent(cva_5y(), accuracy = 0.1))
	valueBox(
    value = cva_5y,
     icon = "fa-plus-square",
     color = ifelse(input$sten_c == 7 | input$pres_c == 0, "grey",
     							 ifelse(cva_5y_numb > 0.2, "red", 
     							 			 ifelse(cva_5y_numb > 0.1, "orange", "green")))
  )
})
```

Row
-------------------------------------------------------------------------------

Rothwell, P M, Z Mehta DPhil, S C Howard DPhil, S A Gutnikov DPhil, and C P Warlow FAcadSci. “From Subgroups to Individuals: General Principles and the Example of Carotid Endarterectomy” 365 (2005): 10.

Row
-------------------------------------------------------------------------------

### CEA POMI

```{r}
cea_pomi = reactive({
	age_1 = ifelse(input$age_c >= 60 & input$age_c < 70, 1, 0)
	age_2 = ifelse(input$age_c >= 70 & input$age_c < 80, 1, 0)
	age_3 = ifelse(input$age_c >= 80, 1, 0)
	ckd_1 = ifelse(input$ckd_c > 1.8 & input$esrd_c != 1, 1, 0)
	ckd_2 = ifelse(input$esrd_c == 1, 1, 0)
	stress_1 = ifelse(input$stress_c == 1, 1, 0)
	stress_2 = ifelse(input$stress_c == 2, 1, 0)
	cad_1 = ifelse(input$cad_c == 1, 1, 0)
	cad_2 = ifelse(input$cad_c == 2, 1, 0)
	dm_1 = ifelse(input$dm_c == 1, 1, 0)
	dm_2 = ifelse(input$dm_c == 2, 1, 0)
	dm_3 = ifelse(input$dm_c == 3, 1, 0)
	chf_1 = ifelse(input$chf_c == 1, 1, 0)
	chf_2 = ifelse(input$chf_c == 2, 1, 0)
	cea_term = -5.82 + 0.44*age_1 + 0.64*age_2 + 1.10*age_3 + 0.76*ckd_1 + 0.64*ckd_2 + 
	-0.15*stress_1 + 0.46*stress_2 + 0.40*cad_1 + 0.76*cad_2 + 0.18*dm_1 + 0.20*dm_2 + 0.39*dm_3 
	0.44*chf_1 + 0.50*chf_2
	cea_pomi = round(
		1/(1+exp(-cea_term)),
		3)
	return(cea_pomi)
})

renderValueBox({
  cea_pomi_numb <- as.numeric(cea_pomi())
  valueBox(
    value = scales::percent(cea_pomi(), accuracy = 0.1),
     icon = "fa-heartbeat",
    color = ifelse(cea_pomi_numb > 0.1, "red", 
    							 ifelse(cea_pomi_numb > 0.05, "orange", "green"))
  )
})
```

Row
-------------------------------------------------------------------------------

Bertges, Daniel J., Dan Neal, Andres Schanzer, Salvatore T. Scali, Philip P. Goodney, Jens Eldrup-Jorgensen, and Jack L. Cronenwett. “The Vascular Quality Initiative Cardiac Risk Index for Prediction of Myocardial Infarction after Vascular Surgery.” Journal of Vascular Surgery 64, no. 5 (November 2016): 1411-1421.e4. https://doi.org/10.1016/j.jvs.2016.04.045.

About
==============================================================================

This app is a collaborative effort to aggregate published risk models into an interface for busy active clinicians.  This is a decision aide and is not intended to supersede clinician or patient preference.  

"All models are wrong, but some are useful."
- George Box

For questions, comments or suggestions please visit the github page: https://github.com/adam-mdmph/vascalc