---
title: "VasCalc"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
runtime: shiny
---

```{r setup, include=FALSE}
library(flexdashboard)
library(dplyr)
```

AAA
=======================================================================

Inputs {.sidebar}
-----------------------------------------------------------------------

### Patient Detials

```{r}

sliderInput("age_a", "Patient Age", min = 18, max = 90, value = 45)
radioButtons("sex_a", "Patient Sex",
 						 choices = list("Male" = 0,
 						 							 "Female" = 1))
radioButtons("race_a", "Patient Race",
  						 choices = list("White" =     0,
						 							    "Non-white" = 1))
radioButtons("indication_a", "Indication for Procedure",
	  					 choices = list("Asymptomatic" =   0,
		  				 							  "Symptomatic" = 1,
	  					 							  "Ruptured" = 2))
sliderInput("diam_a", "Maximal Aorta Diameter", min = 30, max = 100, value = 55)
radioButtons("cad_a", "History of coronary artery disease",
  						 choices = list("None" =                                         0,
  						 							 "History of MI, asymptomatic or stable angina" = 1,
  						 							 "Unstable angina/MI within 6 months" =           2))
radioButtons("cvd_a", "Cerebrovascular Disease",
  						 choices = list("No" =  0,
	  					 						    "Yes" = 1))
radioButtons("copd_a", "COPD",
			  			 choices = list("None" =                         0,
			  			 						    "Not treated or on medication" = 1,
			  			 						    "Home oxygen" =                  2))
radioButtons("ckd_a", "Chronic kidney disease stage",
			  			 choices = list("Cr <1.5" =  0,
						 							    "Cr 1.5-2" = 1,
						 							    "Cr >2" =    2))
```


Row
----------------------------------------------

### Annual Rupture Risk

```{r}
rupture_risk = reactive({
	rupture_risk = ifelse(input$diam_a < 40, "Minimal",
												ifelse(input$diam_a < 50, "1%",
															 ifelse(input$diam_a < 60, "5-10%",
															 			 ifelse(input$diam_a < 70, "10-20%",
															 			 			 ifelse(input$diam_a < 80, "20-40%", "30-50%")))))
	return(rupture_risk)
})

renderValueBox({
  valueBox(
    value = rupture_risk(),
    icon = "fa-bomb",
    color = ifelse(input$diam_a < 40, "green",
												ifelse(input$diam_a < 50, "green",
															 ifelse(input$diam_a < 60, "orange", "red")))
  )
})
```

Row
--------------------------------------------------------------------------------

Chaikof, Elliot L., Ronald L. Dalman, Mark K. Eskandari, Benjamin M. Jackson, W. Anthony Lee, M. Ashraf Mansour, Tara M. Mastracci, et al. “The Society for Vascular Surgery Practice Guidelines on the Care of Patients with an Abdominal Aortic Aneurysm.” Journal of Vascular Surgery 67, no. 1 (January 2018): 2-77.e2. https://doi.org/10.1016/j.jvs.2017.10.044.

Row
-----------------------------------------------

### EVAR 30d Mortality

```{r}
evar_mort_30 = reactive({
	age_1 = ifelse(input$age_a > 75, 1, 0)
	sex_1 = ifelse(input$sex_a == 1, 1, 0)
	cad_1 = ifelse(input$cad_a > 0, 1, 0)
	cvd_1 = ifelse(input$cvd_a == 1, 1, 0)
	copd_1 = ifelse(input$copd_a > 0, 1, 0)
	ckd_1 = ifelse(input$ckd_a == 1, 1, 0)
	ckd_2 = ifelse(input$ckd_a == 2, 1, 0)
	diam_1 = ifelse(input$diam_a > 65, 1, 0)
	evar_term = -6.76 + 0.78*age_1 + 0.69*sex_1 + 0.56*cad_1 + 0.71*cvd_1 + 0.95*copd_1 + 
		0.89*ckd_1 + 1.31*ckd_2 + 0.91*diam_1
	evar_mort_30 = round(
		100/(1+exp(-evar_term)),
		2)
	return(evar_mort_30)
})

renderValueBox({
  evar_mort_30 <- formatC(evar_mort_30(), digits = 1, format = "f")
  evar_mort_30_numb <- as.numeric(evar_mort_30())
  valueBox(
    value = evar_mort_30,
    icon = "fa-syringe",
    color = ifelse(evar_mort_30_numb > 10, "red", 
    							 ifelse(evar_mort_30_numb > 5, "orange", "green"))
  )
})
```

### Open (Infrarenal Clamp) 30d Mortality

```{r}
iraaa_mort_30 = reactive({
	age_1 = ifelse(input$age_a > 75, 1, 0)
	sex_1 = ifelse(input$sex_a == 1, 1, 0)
	cad_1 = ifelse(input$cad_a > 0, 1, 0)
	cvd_1 = ifelse(input$cvd_a == 1, 1, 0)
	copd_1 = ifelse(input$copd_a > 0, 1, 0)
	ckd_1 = ifelse(input$ckd_a == 1, 1, 0)
	ckd_2 = ifelse(input$ckd_a == 2, 1, 0)
	diam_1 = ifelse(input$diam_a == 1, 1, 0)
	iraaa_term = -6.76 + 1.08 + 0.78*age_1 + 0.69*sex_1 + 0.56*cad_1 + 0.71*cvd_1 + 0.95*copd_1 + 
		0.89*ckd_1 + 1.31*ckd_2 + 0.91*diam_1
	iraaa_mort_30 = round(
		100/(1+exp(-iraaa_term)),
		2)
	return(iraaa_mort_30)
})

renderValueBox({
  iraaa_mort_30 <- formatC(iraaa_mort_30(), digits = 1, format = "f")
  iraaa_mort_30_numb <- as.numeric(iraaa_mort_30())
  valueBox(
    value = iraaa_mort_30,
    icon = "fa-user-ninja",
    color = ifelse(iraaa_mort_30_numb < 5, "green", 
    							 ifelse(iraaa_mort_30_numb < 10, "orange", "red"))
  )
})
```

### Open (Supra-renal Clamp) 30d Mortality

```{r}
sraaa_mort_30 = reactive({
	age_1 = ifelse(input$age_a > 75, 1, 0)
	sex_1 = ifelse(input$sex_a == 1, 1, 0)
	cad_1 = ifelse(input$cad_a > 0, 1, 0)
	cvd_1 = ifelse(input$cvd_a == 1, 1, 0)
	copd_1 = ifelse(input$copd_a > 0, 1, 0)
	ckd_1 = ifelse(input$ckd_a == 1, 1, 0)
	ckd_2 = ifelse(input$ckd_a == 2, 1, 0)
	diam_1 = ifelse(input$diam_a == 1, 1, 0)
	sraaa_term = -6.76 + 1.905 + 0.78*age_1 + 0.69*sex_1 + 0.56*cad_1 + 0.71*cvd_1 + 0.95*copd_1 + 
		0.89*ckd_1 + 1.31*ckd_2 + 0.91*diam_1
	sraaa_mort_30 = round(
		100/(1+exp(-sraaa_term)),
		2)
	return(sraaa_mort_30)
})

renderValueBox({
  sraaa_mort_30 <- formatC(sraaa_mort_30(), digits = 1, format = "f")
  sraaa_mort_30_numb <- as.numeric(sraaa_mort_30())
  valueBox(
    value = sraaa_mort_30,
    icon = "fa-user-ninja",
    color = ifelse(sraaa_mort_30_numb > 10, "red", 
    							 ifelse(sraaa_mort_30_numb > 5, "orange", "green"))
  )
})
```

Row
-------------------------------------------------------------------------------
Eslami, Mohammad H., Denis Rybin, Gheorghe Doros, Jeffrey A. Kalish, and Alik Farber. “Comparison of a Vascular Study Group of New England Risk Prediction Model with Established Risk Prediction Models of In-Hospital Mortality after Elective Abdominal Aortic Aneurysm Repair.” Journal of Vascular Surgery 62, no. 5 (November 2015): 1125-1133.e2. https://doi.org/10.1016/j.jvs.2015.06.051.


CLTI
===============================================================================

Inputs {.sidebar}
-------------------------------------------------------------------------------

### Patient Detials

```{r}

radioButtons("age_p", "Patient Age", 
						   choices = list("<60 Years" =   0,
						 	  						  "60-70 Years" = 1,
						 		  					  "71-80 Years" = 2,
						 			  				  ">80 Years" =   3))
radioButtons("race_p", "Patient Race",
  						 choices = list("White" =     0,
						 							    "Non-white" = 1))
radioButtons("indication_p", "Indication for Procedure",
	  					 choices = list("Rest pain" =   0,
		  				 							  "Tissue loss" = 1))
radioButtons("cad_p", "History of coronary artery disease",
				   		 choices = list("None" =                                         0,
		  				 						    "History of MI, asymptomatic or stable angina" = 1,
	  					 							  "Unstable angina/MI within 6 months" =           2))
radioButtons("chf_p", "Congestive Heart Failure",
  						 choices = list("No" =  0,
	  					 						    "Yes" = 1))
radioButtons("copd_p", "COPD",
			  			 choices = list("None" =                         0,
			  			 						    "Not treated or on medication" = 1,
			  			 						    "Home oxygen" =                  2))
radioButtons("ckd_p", "Chronic kidney disease stage",
			  			 choices = list("1 (GFR >90 mL/min/1.73 m2)" =    0,
						 							    "2 (GFR 60-89 mL/min/1.73 m2)" =  1,
						 							    "3 (GFR 30-59 mL/min/1.73 m2)" =  2,
						 						      "4 (GFR 15-29 mL/min/1.73 m2)" =  3,
						 						      "5 (GFR <15 mL/min/1.73 m2)" =    4))
radioButtons("ambulation_p", "Ambulation Status",
						   choices = list("Independent" =      0,
						 						     	"With Assistance" =  1,
						 							    "Wheelchair bound" = 2,
						 							    "Bedbound" =         3))
radioButtons("statin_p", "Pre-opreative medications: Statin",
						   choices = list("No" =  0,
						 							    "Yes" = 1))
```

Row
----------------------------------------------------------



About
==============================================================================

This app is a collaborative effort to aggregate published risk models into an interface for busy active clinicians.  This is a decision aide and is not intended to supersede clinician or patient preference.  

"All models are wrong, but some are useful."
- George Box

For questions, comments or suggestions please visit the github page: https://github.com/adam-mdmph/vascalc