---
title: "VasCalc"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
runtime: shiny
---

```{r setup, include=FALSE}
library(flexdashboard)
library(dplyr)
library(scales)
```

eAAA
=======================================================================

Inputs {.sidebar}
-----------------------------------------------------------------------


```{r}
sliderInput("age_a", "Patient Age", min = 18, max = 90, value = 45)
selectInput("sex_a", "Patient Sex",
 						 choices = list("Male" = 0,
 						 							 "Female" = 1))
sliderInput("diam_a", "Maximal Aorta Diameter", min = 30, max = 100, value = 55)
selectInput("renalclamp_a", "Suprarenal clamp?",
						 choices = list("Unlikely" = 0,
						 							 "Likely" = 1))
selectInput("cad_a", "History of coronary artery disease",
  						 choices = list("None" =                                         0,
  						 							 "History of MI, asymptomatic or stable angina" = 1,
  						 							 "Unstable angina/MI within 6 months" =           2))
selectInput("chf_a", "Congestive Heart Failure",
  						 choices = list("None" =  0,
	  					 						    "Asymptomatic" = 1,
  						 							 "Symptomatic" = 2))
selectInput("stress_a", "Stress Test",
						 choices = list ("Not Performed" = 0,
						 								"Normal" = 1,
						 								"Abnormal" = 2))
selectInput("cvd_a", "Cerebrovascular Disease",
  						 choices = list("No" =  0,
	  					 						    "Yes" = 1))
selectInput("copd_a", "COPD",
			  			 choices = list("None" =                         0,
			  			 						    "Not treated or on medication" = 1,
			  			 						    "Home oxygen" =                  2))
selectInput("dm_a", "Diabetes",
						 choices = list("None" = 0,
						 							 "Diet Controlled" = 1,
						 							 "Noninsulin Medication" = 2,
						 							 "Insulin Dependent" = 3))
selectInput("esrd_a", "ESRD on Dialysis",
						 choices = list("No" = 0,
						 							 "Yes" = 1))
sliderInput("ckd_a", "Creatinine (mg/dL), not on dialysis", min = 0.5, max = 4.0, value = 1.0)
```


Row
----------------------------------------------

### Annual Rupture Risk

```{r}
rupture_risk = reactive({
	rupture_risk = ifelse(input$diam_a < 40, "0.3%",
												ifelse(input$diam_a < 50, "0.5-1.5%",
															 ifelse(input$diam_a < 60, "1-11%",
															 			 ifelse(input$diam_a < 70, "11-22%", ">30%"))))
	return(rupture_risk)
})

renderValueBox({
  valueBox(
    value = rupture_risk(),
    icon = "fa-bomb",
    color = ifelse(input$diam_a < 40, "green",
												ifelse(input$diam_a < 50, "green",
															 ifelse(input$diam_a < 60, "orange", "red")))
  )
})
```

Row
--------------------------------------------------------------------------------

Tracci MC, Roy RR, Upchurch GR. "Aortoiliac Aneurysms: Evaluation, Decision Making, and Medical Management." Rutherford's Vascular Surgery and Endovascular Therapy. 9th Ed. Edited by Sidway AN and Perler BA. 2019.  Chapter 70, 884-893.e3

Row
-----------------------------------------------

### EVAR 30d Mortality

```{r}
evar_mort_30 = reactive({
	age_1 = ifelse(input$age_a > 75, 1, 0)
	sex_1 = ifelse(input$sex_a == 1, 1, 0)
	cad_1 = ifelse(input$cad_a > 0, 1, 0)
	cvd_1 = ifelse(input$cvd_a == 1, 1, 0)
	copd_1 = ifelse(input$copd_a > 0, 1, 0)
	ckd_1 = ifelse(input$ckd_a >= 1.5 & input$ckd_a <=2 & input$esrd_a == 0, 1, 0)
	ckd_2 = ifelse(input$ckd_a > 2 | input$esrd_a == 1, 1, 0)
	diam_1 = ifelse(input$diam_a > 65, 1, 0)
	evar_term = -6.76 + 0.78*age_1 + 0.69*sex_1 + 0.56*cad_1 + 0.71*cvd_1 + 0.95*copd_1 + 
		0.89*ckd_1 + 1.31*ckd_2 + 0.91*diam_1
	evar_mort_30 = round(
		1/(1+exp(-evar_term)),
		3)
	return(evar_mort_30)
})

renderValueBox({
  evar_mort_30_numb <- as.numeric(evar_mort_30())
  valueBox(
    value = scales::percent(evar_mort_30(), accuracy = 0.1),
    icon = "fa-syringe",
    color = ifelse(evar_mort_30_numb > 0.1, "red", 
    							 ifelse(evar_mort_30_numb > 0.05, "orange", "green"))
  )
})
```

### Open AAA 30d Mortality

```{r}
open_mort_30 = reactive({
	age_1 = ifelse(input$age_a > 75, 1, 0)
	sex_1 = ifelse(input$sex_a == 1, 1, 0)
	cad_1 = ifelse(input$cad_a > 0, 1, 0)
	cvd_1 = ifelse(input$cvd_a == 1, 1, 0)
	copd_1 = ifelse(input$copd_a > 0, 1, 0)
	ckd_1 = ifelse(input$ckd_a >= 1.5 & input$ckd_a <=2 & input$esrd_a == 0, 1, 0)
	ckd_2 = ifelse(input$ckd_a > 2 | input$esrd_a == 1, 1, 0)
	diam_1 = ifelse(input$diam_a == 1, 1, 0)
	renalclamp_1 = ifelse(input$renalclamp_a == 1, 1, 0)
	renalclamp_2 = ifelse(input$renalclamp_a == 2, 1, 0)
	open_term = -6.76 + 0.78*age_1 + 0.69*sex_1 + 0.56*cad_1 + 0.71*cvd_1 + 0.95*copd_1 + 
		0.89*ckd_1 + 1.31*ckd_2 + 0.91*diam_1 + 1.08*renalclamp_1 + 1.905*renalclamp_2
	open_mort_30 = round(
		1/(1+exp(-open_term)),
		3)
	return(open_mort_30)
})

renderValueBox({
  open_mort_30_numb <- as.numeric(open_mort_30())
  valueBox(
    value = scales::percent(open_mort_30(), accuracy = 0.1),
    icon = "fa-user-ninja",
    color = ifelse(open_mort_30_numb < 0.1, "green", 
    							 ifelse(open_mort_30_numb < 0.05, "orange", "red"))
  )
})
```

Row
-------------------------------------------------------------------------------
Eslami, Mohammad H., Denis Rybin, Gheorghe Doros, Jeffrey A. Kalish, and Alik Farber. “Comparison of a Vascular Study Group of New England Risk Prediction Model with Established Risk Prediction Models of In-Hospital Mortality after Elective Abdominal Aortic Aneurysm Repair.” Journal of Vascular Surgery 62, no. 5 (November 2015): 1125-1133.e2. https://doi.org/10.1016/j.jvs.2015.06.051.

Row
-------------------------------------------------------------------------------

### EVAR POMI

```{r}
evar_pomi = reactive({
	age_1 = ifelse(input$age_a >= 60 & input$age_a < 70, 1, 0)
	age_2 = ifelse(input$age_a >= 70 & input$age_a < 80, 1, 0)
	age_3 = ifelse(input$age_a >= 80, 1, 0)
	ckd_1 = ifelse(input$ckd_a > 1.8 & input$esrd_a != 1, 1, 0)
	ckd_2 = ifelse(input$esrd_a ==1, 1, 0)
	stress_1 = ifelse(input$stress_a == 1, 1, 0)
	stress_2 = ifelse(input$stress_a == 2, 1, 0)
	cad_1 = ifelse(input$cad_a == 1, 1, 0)
	cad_2 = ifelse(input$cad_a == 2, 1, 0)
	dm_1 = ifelse(input$dm_a == 1, 1, 0)
	dm_2 = ifelse(input$dm_a == 2, 1, 0)
	dm_3 = ifelse(input$dm_a == 3, 1, 0)
	chf_1 = ifelse(input$chf_a == 1, 1, 0)
	chf_2 = ifelse(input$chf_a == 2, 1, 0)
	evar_term = -5.82 + 0.17 + 0.44*age_1 + 0.64*age_2 + 1.10*age_3 + 0.76*ckd_1 + 0.64*ckd_2 + 
	-0.15*stress_1 + 0.46*stress_2 + 0.40*cad_1 + 0.76*cad_2 + 0.18*dm_1 + 0.20*dm_2 + 0.39*dm_3 
	0.44*chf_1 + 0.50*chf_2
	evar_pomi = round(
		1/(1+exp(-evar_term)),
		3)
	return(evar_pomi)
})

renderValueBox({
  evar_pomi_numb <- as.numeric(evar_pomi())
  valueBox(
    value = scales::percent(evar_pomi(), accuracy = 0.1),
     icon = "fa-heartbeat",
    color = ifelse(evar_pomi_numb > 0.1, "red", 
    							 ifelse(evar_pomi_numb > 0.05, "orange", "green"))
  )
})
```

### Open AAA POMI

```{r}
open_pomi = reactive({
	age_1 = ifelse(input$age_a >= 60 & input$age_a < 70, 1, 0)
	age_2 = ifelse(input$age_a >= 70 & input$age_a < 80, 1, 0)
	age_3 = ifelse(input$age_a >= 80, 1, 0)
	ckd_1 = ifelse(input$ckd_a > 1.8 & input$esrd_a != 1, 1, 0)
	ckd_2 = ifelse(input$esrd_a == 1, 1, 0)
	stress_1 = ifelse(input$stress_a == 1, 1, 0)
	stress_2 = ifelse(input$stress_a == 2, 1, 0)
	cad_1 = ifelse(input$cad_a == 1, 1, 0)
	cad_2 = ifelse(input$cad_a == 2, 1, 0)
	dm_1 = ifelse(input$dm_a == 1, 1, 0)
	dm_2 = ifelse(input$dm_a == 2, 1, 0)
	dm_3 = ifelse(input$dm_a == 3, 1, 0)
	chf_1 = ifelse(input$chf_a == 1, 1, 0)
	chf_2 = ifelse(input$chf_a == 2, 1, 0)
	open_term = -5.82 + 1.91 + 0.44*age_1 + 0.64*age_2 + 1.10*age_3 + 0.76*ckd_1 + 0.64*ckd_2 + 
	-0.15*stress_1 + 0.46*stress_2 + 0.40*cad_1 + 0.76*cad_2 + 0.18*dm_1 + 0.20*dm_2 + 0.39*dm_3 
	0.44*chf_1 + 0.50*chf_2
	open_pomi = round(
		1/(1+exp(-open_term)),
		3)
	return(open_pomi)
})

renderValueBox({
  open_pomi_numb <- as.numeric(open_pomi())
  valueBox(
    value = scales::percent(open_pomi(), accuracy = 0.1),
     icon = "fa-heartbeat",
    color = ifelse(open_pomi_numb > 0.1, "red", 
    							 ifelse(open_pomi_numb > 0.05, "orange", "green"))
  )
})
```

Row
-------------------------------------------------------------------------------

Bertges, Daniel J., Dan Neal, Andres Schanzer, Salvatore T. Scali, Philip P. Goodney, Jens Eldrup-Jorgensen, and Jack L. Cronenwett. “The Vascular Quality Initiative Cardiac Risk Index for Prediction of Myocardial Infarction after Vascular Surgery.” Journal of Vascular Surgery 64, no. 5 (November 2016): 1411-1421.e4. https://doi.org/10.1016/j.jvs.2016.04.045.

rAAA
===============================================================================

CLTI
===============================================================================

Inputs {.sidebar}
-------------------------------------------------------------------------------

### Patient Details

```{r}

radioButtons("age_p", "Patient Age", 
						   choices = list("<60 Years" =   0,
						 	  						  "60-70 Years" = 1,
						 		  					  "71-80 Years" = 2,
						 			  				  ">80 Years" =   3))
radioButtons("race_p", "Patient Race",
  						 choices = list("White" =     0,
						 							    "Non-white" = 1))
radioButtons("indication_p", "Indication for Procedure",
	  					 choices = list("Rest pain" =   0,
		  				 							  "Tissue loss" = 1))
radioButtons("cad_p", "History of coronary artery disease",
				   		 choices = list("None" =                                         0,
		  				 						    "History of MI, asymptomatic or stable angina" = 1,
	  					 							  "Unstable angina/MI within 6 months" =           2))
radioButtons("chf_p", "Congestive Heart Failure",
  						 choices = list("No" =  0,
	  					 						    "Yes" = 1))
radioButtons("copd_p", "COPD",
			  			 choices = list("None" =                         0,
			  			 						    "Not treated or on medication" = 1,
			  			 						    "Home oxygen" =                  2))
radioButtons("ckd_p", "Chronic kidney disease stage",
			  			 choices = list("1 (GFR >90 mL/min/1.73 m2)" =    0,
						 							    "2 (GFR 60-89 mL/min/1.73 m2)" =  1,
						 							    "3 (GFR 30-59 mL/min/1.73 m2)" =  2,
						 						      "4 (GFR 15-29 mL/min/1.73 m2)" =  3,
						 						      "5 (GFR <15 mL/min/1.73 m2)" =    4))
radioButtons("ambulation_p", "Ambulation Status",
						   choices = list("Independent" =      0,
						 						     	"With Assistance" =  1,
						 							    "Wheelchair bound" = 2,
						 							    "Bedbound" =         3))
radioButtons("statin_p", "Pre-opreative medications: Statin",
						   choices = list("No" =  0,
						 							    "Yes" = 1))
```

Row
----------------------------------------------------------

Carotid
==============================================================================

Input {.sidebar}
------------------------------------------------------------------------------

### Patient Details

```{r}
sliderInput("age_c", "Patient Age", min = 18, max = 90, value = 45)
selectInput("sex_c", "Patient Sex",
 						 choices = list("Male" = 0,
 						 							 "Female" = 1))
selectInput("pres_c", "Primary Symptomatic Event",
						choices = list("Asymptomatic" = 0,
													 "Monocular" = 1,
													 "Single Cerebral TIA" = 2,
													 "Multiple Cerebral TIA" = 3,
													 "Minor Stroke" = 4,
													 "Major Disabling Stroke" = 5))
sliderInput("time_c", "Time Since Last Event", min = 1, max = 180, value = 7)
selectInput("sten_c", "Percent Stenosis",
						choices = list("<50%" = 0,
						              "50-59" = 1,
													 "60-69%" = 2,
													 "70-79%" = 3,
													 "80-89%" = 4,
													 "90-99%" = 5,
													 "Near Occlusion" = 6,
													 "Occluded" = 7))
selectInput("ulc_c", "Ulcerated Plaque",
						choices = list("No" = 0,
													 "Yes" = 1))
selectInput("htn_c", "Hypertension on medications",
						choices = list("No" = 0,
													 "Yes" = 1))
selectInput("cad_c", "History of coronary artery disease",
  						 choices = list("None" =                                         0,
  						 							 "History of MI, asymptomatic or stable angina" = 1,
  						 							 "Unstable angina/MI within 6 months" =           2))
selectInput("chf_c", "Congestive Heart Failure",
  						 choices = list("None" =  0,
	  					 						    "Asymptomatic" = 1,
  						 							 "Symptomatic" = 2))
selectInput("stress_c", "Stress Test",
						 choices = list ("Not Performed" = 0,
						 								"Normal" = 1,
						 								"Abnormal" = 2))
selectInput("pvd_c", "Peripheral Vascular Disease",
  						 choices = list("No" =  0,
	  					 						    "Yes" = 1))
selectInput("copd_c", "COPD",
			  			 choices = list("None" =                         0,
			  			 						    "Not treated or on medication" = 1,
			  			 						    "Home oxygen" =                  2))
selectInput("dm_c", "Diabetes",
						 choices = list("None" = 0,
						 							 "Diet Controlled" = 1,
						 							 "Noninsulin Medication" = 2,
						 							 "Insulin Dependent" = 3))
selectInput("esrd_c", "ESRD on Dialysis",
						 choices = list("No" = 0,
						 							 "Yes" = 1))
sliderInput("ckd_c", "Creatinine (mg/dL), not on dialysis", min = 0.5, max = 4.0, value = 1.0)
```

Row
-------------------------------------------------------------------------------

### 5-year risk of ipsilateral stroke (UNDER CONSTRUCTION)

```{r}
cva_5y = reactive({
	sten_1 = as.numeric(ifelse(input$sten_c < 6, input$sten_c, 0))
	nearocc_l = ifelse(input$sten_c == 6, 1, 0)
	sex_1 = ifelse(input$sex_c == 0, 1, 0)
	age_1 = as.numeric(input$age_c/10)
	time_1 = as.numeric(input$time_c/7)
	pres_1 = ifelse(input$pres_c == 2, 1, 0)
	pres_2 = ifelse(input$pres_c == 3, 1, 0)
	pres_3 = ifelse(input$pres_c == 4, 1, 0)
	pres_4 = ifelse(input$pres_c == 5, 1, 0)
	dm_1 = ifelse(input$dm_c > 0, 1, 0)
	cad_1 = ifelse(input$cad_c > 0, 1, 0)
	pvd_1 = ifelse(input$pvd_c == 1, 1, 0)
	htn_1 = ifelse(input$htn_c == 1, 1, 0)
	ulc_1 = ifelse(input$ulc_c == 1, 1, 0)
	cva_5y_term = -3.55 + log(1.18)*sten_1 + log(0.49)*nearocc_l + log(1.19)*sex_1 + log(1.12)*age_1 +
		log(0.96)*time_1 + log(1.41)*pres_1 + log(2.05)*pres_2 + log(1.82)*pres_3 + log(2.54)*pres_4 + log(1.35)*dm_1 +
		log(1.57)*cad_1 + log(1.24)*htn_1 + log(2.03)*ulc_1
	cva_5y = round(
		1/(1+exp(-cva_5y_term)),
		3)
	return(cva_5y)
})

renderValueBox({
  cva_5y_numb <- as.numeric(cva_5y())
  cva_5y = ifelse(input$sten_c == 7 | input$pres_c == 0, "Unable to calculate", 
    						scales::percent(cva_5y(), accuracy = 0.1))
	valueBox(
    value = cva_5y,
     icon = "fa-plus-square",
     color = ifelse(input$sten_c == 7 | input$pres_c == 0, "grey",
     							 ifelse(cva_5y_numb > 0.2, "red", 
     							 			 ifelse(cva_5y_numb > 0.1, "orange", "green")))
  )
})
```

Row
-------------------------------------------------------------------------------

Rothwell, P M, Z Mehta DPhil, S C Howard DPhil, S A Gutnikov DPhil, and C P Warlow FAcadSci. “From Subgroups to Individuals: General Principles and the Example of Carotid Endarterectomy” 365 (2005): 10.

Row
-------------------------------------------------------------------------------

### CEA POMI

```{r}
cea_pomi = reactive({
	age_1 = ifelse(input$age_c >= 60 & input$age_c < 70, 1, 0)
	age_2 = ifelse(input$age_c >= 70 & input$age_c < 80, 1, 0)
	age_3 = ifelse(input$age_c >= 80, 1, 0)
	ckd_1 = ifelse(input$ckd_c > 1.8 & input$esrd_c != 1, 1, 0)
	ckd_2 = ifelse(input$esrd_c == 1, 1, 0)
	stress_1 = ifelse(input$stress_c == 1, 1, 0)
	stress_2 = ifelse(input$stress_c == 2, 1, 0)
	cad_1 = ifelse(input$cad_c == 1, 1, 0)
	cad_2 = ifelse(input$cad_c == 2, 1, 0)
	dm_1 = ifelse(input$dm_c == 1, 1, 0)
	dm_2 = ifelse(input$dm_c == 2, 1, 0)
	dm_3 = ifelse(input$dm_c == 3, 1, 0)
	chf_1 = ifelse(input$chf_c == 1, 1, 0)
	chf_2 = ifelse(input$chf_c == 2, 1, 0)
	cea_term = -5.82 + 0.44*age_1 + 0.64*age_2 + 1.10*age_3 + 0.76*ckd_1 + 0.64*ckd_2 + 
	-0.15*stress_1 + 0.46*stress_2 + 0.40*cad_1 + 0.76*cad_2 + 0.18*dm_1 + 0.20*dm_2 + 0.39*dm_3 
	0.44*chf_1 + 0.50*chf_2
	cea_pomi = round(
		1/(1+exp(-cea_term)),
		3)
	return(cea_pomi)
})

renderValueBox({
  cea_pomi_numb <- as.numeric(cea_pomi())
  valueBox(
    value = scales::percent(cea_pomi(), accuracy = 0.1),
     icon = "fa-heartbeat",
    color = ifelse(cea_pomi_numb > 0.1, "red", 
    							 ifelse(cea_pomi_numb > 0.05, "orange", "green"))
  )
})
```

Row
-------------------------------------------------------------------------------

Bertges, Daniel J., Dan Neal, Andres Schanzer, Salvatore T. Scali, Philip P. Goodney, Jens Eldrup-Jorgensen, and Jack L. Cronenwett. “The Vascular Quality Initiative Cardiac Risk Index for Prediction of Myocardial Infarction after Vascular Surgery.” Journal of Vascular Surgery 64, no. 5 (November 2016): 1411-1421.e4. https://doi.org/10.1016/j.jvs.2016.04.045.

About
==============================================================================

This app is a collaborative effort to aggregate published risk models into an interface for busy active clinicians.  This is a decision aide and is not intended to supersede clinician or patient preference.  

"All models are wrong, but some are useful."
- George Box

For questions, comments or suggestions please visit the github page: https://github.com/adam-mdmph/vascalc